%\documentclass[a4paper,preprint, fleqn]{aastex}
%\documentclass[a4paper, preprint, fleqn, usenatbib]{aastex}
\documentclass[fleqn, usenatbib]{mnras}
\usepackage{graphicx}   % Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{color,verbatim,url}
\usepackage{tabularx}
\usepackage[table,usenames,dvipsnames]{xcolor}
\usepackage{pdflscape}
\usepackage{lastpage}
\usepackage{newtxtext, newtxmath}

\usepackage[T1]{fontenc}
\usepackage{ae, aecompl}

\definecolor{pink}{rgb}{0.858, 0.188, 0.478}
\definecolor{purple}{RGB}{76, 0,153}

\newcommand{\red}[1]{{\color{red}{#1}}}
\newcommand{\green}[1]{{\color{green}{#1}}}
\newcommand{\blue}[1]{{\color{blue}{#1}}}
\newcommand{\x}{\vec{x}}
\renewcommand{\d}[0]{{\rm d}}
\newcommand{\shahab}[1]{\textcolor{pink}{\bf #1}}

\newcommand{\be}{\begin{equation}}  \newcommand{\ee}{\end{equation}}
\newcommand{\mb}[1]{\mbox{ #1 }}  
\newcommand{\ba}{\begin{eqnarray}}\newcommand{\ea}{\end{eqnarray}}
\newcommand{\bm}[1]{\mbox{\boldmath{$#1$}}}   %this is bold italic for MNRAS
%\newcommand{\mat}[1]{\mathbfss{#1}}
\newcommand{\diff}{\mathrm{d}}

\title[Comment on `The Limits of Cosmic Shear']{Comment on `The Limits of Cosmic Shear'}

\input{authors}

\date{Released 16/12/2016}

\pagerange{\pageref{firstpage}--\pageref{LastPage}} \pubyear{2016}

\begin{document}
\setlength{\voffset}{-12mm}

\label{firstpage}

\maketitle

\begin{abstract}

%\author{Members of the KiDS, CFHTLenS and RCSLenS collaborations; \\
%J. Harnois-D\'eraps, C. Heymans, H. Hildebrandt, S. Joudaki,  M. Kilbinger, F. K\"ohlinger, K. Kuijken, P. Schneider, P. Simon, L. Van Waerbeke, M. Viola}%

Kitching et al. (2016) examine the impact of the flat-sky and Limber approximations that can be used when constraining cosmological parameters from the measurement of weak gravitational lensing by large-scale structures, also known as cosmic shear.  We support the core message of this paper that the use of such approximations should be considered in the future analyses of high precision surveys such as Euclid, LSST and WFIRST.  In this comment, we argue that these approximations have negligible impact for current surveys and are thus unable to significantly reduce the tension between the constraints from some current weak lensing surveys and the Planck CMB experiment.  Reducing uncertainty and characterising bias in photometric redshift estimation is a critical task for the success of current and future surveys.  We highlight that sophisticated treatments of these uncertainties have already been explored in the literature and have been shown not to resolve the tension with Planck, in contrast to the message that Kitching et al. (2016) convey.

\end{abstract}

\begin{keywords}
cosmology: observations -- gravitational lensing: weak -- galaxies: photometry -- surveys
\end{keywords}


\section{Introduction}

The measurement of weak gravitational lensing by large-scale structures provides a powerful cosmological probe of dark matter, dark energy, and modifications to gravity.  As such it is the primary science goal of several current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys. Interest in the results from these surveys is high as statistically significant deviations have been found between the cosmological parameter constraints from the CMB Planck experiment \citep{planck/cosmo:2015} in comparison to weak lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{hildebrandt/etal:2016} and the Canada-France-Hawaii Telescope Lensing Survey \citep[CFHTLenS;][] {joudaki/etal:2016}.  If the source of this tension is not a result of so-far unconsidered sources of systematic errors in one or all experiments, extensions to the standard flat $\Lambda$CDM cosmological models need to be considered.  \citet{joudaki/etal:2017} have shown, for example, that the tension can be resolved with an evolving dark energy model.

In this comment paper we discuss the flat-sky and Limber approximations that can be used when deriving theoretical predictions for the principally used cosmic shear statistic, $\xi_\pm$, the two-point shear correlation functions.  \citet{kitching/etal:2016} report that when considering the flat-sky and Limber approximations in concert, tensions between weak lensing and CMB experiments can be reduced. They illustrate the effect with a re-analysis of the non-tomographic weak lensing data from the CFHTLenS survey \citep{kilbinger/etal:2013}.    On initial inspection we found that these claims appeared implausible, for two reasons: First, in a naive estimate, the deviation of a flat-sky approximation from a full treatment is expected to be of a similar order to the fractional difference between $\theta_{\rm max}$ and $\sin\theta_{\rm max}$,
where $\theta_{\rm max}$ is the maximum angular scale considered in the cosmic shear analysis. In the case of \citet{hildebrandt/etal:2016}, where $\theta_{\rm max}=50$ arcmin, $(\theta_{\rm max} - \sin\theta_{\rm max})/\theta_{\rm max} \approx 3.5 \times 10^{-5}$.  Second, it was shown in \citet[][see their Fig.3]{giannantonio/etal:2012} that the difference between the Limber approximated shear power spectrum and one calculated using an exact treatment is far smaller than cosmic variance, even for a full-sky cosmic shear survey.

This comment seeks to explore the content of \citet{kitching/etal:2016} in detail, discussing why we disagree with their findings.  It is structured as follows.  In section~\ref{sec:theory} we clarify which brand of approximations, highlighted by \citet{kitching/etal:2016}, have been used in recent weak lensing analyses \citep{joudaki/etal:2016, hildebrandt/etal:2016, joudaki/etal:2017}.  We are unable to replicate key results from \citet{kitching/etal:2016} and show that we do not expect these approximations to impact on the cosmological analysis of current surveys.  In section~\ref{sec:cfhtlens} we present a `one-parameter' cosmological re-analysis of 2D cosmic shear data from \citet{kilbinger/etal:2013} which is inconsistent with the analysis presented in \citet{kitching/etal:2016}.  We also briefly review the literature that has advanced our understanding since the original CFHTLenS analyses were published and discuss the impact of flat-sky and Limber approximations in our analysis of numerical simulations, CMB lensing and quadratic estimators for the cosmic shear power spectrum.

In section~\ref{sec:photoz} we review our current knowledge of photometric redshift uncertainties and the sophisticated mitigation strategies that have already been applied to data.  We suggest that a possible misinterpretation in the sign of the redshift biases reported in \citet{choi/etal:2016} has led to the incorrect conclusion of \citet{kitching/etal:2016} that these redshift biases can resolve the tension with Planck.  

\section{Theory}
\label{sec:theory}
\input{theory.tex}

\section{Advances in understanding since CFHTLenS}
\label{sec:cfhtlens}
\input{cfhtlens.tex}

\section{Photometric redshift bias and uncertainty}
\label{sec:photoz}
\input{photoz.tex}

\section{Conclusion}
\label{sec:conclusion}
\input{conclusion.tex}

\bibliographystyle{apj}
\bibliography{Limber_Comment}
\end{document}
